\vfill A Testing Framework for Web Applications

### 2014-03-16 Paper/paper.tex
Added TODOs, added section heading for UI testing, expanded Nightwatch

%%%%%%%%%%%%%%%%
%%% Abstract 
%%% VERY General overview of problem and solution in paper
%%%%%%%%%%%%%%%%
\begin{abstract}
We have brought together a number of testing tools from the web and created what we feel is a fully-featured, easy to use, testing framework for web applications.
\end{abstract}

@@

- Talk about GeoLocation

- TIE JS PORTION INTO THIS

@@

@@

@@

NO WEB PAGE TESTING SO FAR

@@

@@

\subsubsection{Nightwatchjs\cite{NightwatchJS}}
Nightwatch is a Javascript testing library that wraps Selenium in an effort to make browser testing more concise and easier to use. Tests are written as a long chain of function calls that produce an easy-to-read series of browser events. Nightwatch uses Node.js' assertion library paired with Selenium's WebDriver to both run browser automation and also report test results.

>>>>

%%%%%%%%%%%%%%%%
%%% Abstract 
%%% VERY General overview of problem and solution in paper
%%%%%%%%%%%%%%%%
\begin{abstract}
\todo{Make this better}
We have brought together a number of testing tools from the web and created what we feel is a fully-featured, easy to use, testing framework for web applications.
\end{abstract}

@@

\todo{Talk about GeoLocation}

\todo{TIE JS PORTION INTO THIS}

@@

\todo{Wrap up?}

@@

An important distinction that needs to be made is that in web applications there is functionality behind the scenes and there is the UI element of the web page. Unit testing frameworks

@@

@@

\subsection{Browser and UI Testing}
Web applications, for the most part, require user input in order to be useful. The way the user interacts is through the outward facing web pages. Testing of a web application would be incomplete without testings the interactions and elements of these web pages. It's important that the inner workings are running the right code and producing the right answer, but it's almost just as important that the parameters get passed correctly and from the right places on the web pages. Also, it is important that navigation work as expected or a user will become frustrated and lose interest in the application.

What's important in browser testing is repeatability and being able to test on multiple browsers. Without the ability to automatically repeat tests, developers are left manually clicking through web pages every time anything changes. In addition, because there are so many different browsers and browser versions in the wild, it's important that the web pages run correctly (and predictably) on as many of them as possible.

@@

\subsubsection{Nightwatchjs\cite{NightwatchJS}}
Nightwatch is a Javascript testing library that wraps Selenium in an effort to make browser testing more concise and straightforward. Nightwatch uses Node.js' assertion library paired with Selenium's WebDriver to both run browser automation and also report test results.

Tests are written as a long chain of function calls that produce an easy-to-read series of browser events. For example, the following code segment opens a browser, goes to google.com, makes some assertions, writes ``nightwatch'' in the search box, clicks the search button, and then makes a few more assertions:
\begin{lstlisting}
module.exports = {
  "Demo test Google" : function (client) {
    client
      .url("http://www.google.com")
      .waitForElementVisible("body", 1000)
      .assert.title("Google")
      .assert.visible("input[type=text]")
      .setValue("input[type=text]", "nightwatch")
      .waitForElementVisible("button[name=btnG]", 1000)
      .click("button[name=btnG]")
      .pause(1000)
      .assert.containsText("#main", "The Night Watch")
      .end();
  }
};
\end{lstlisting}
As you can see, just reading the code line by line paints a picture of exactly what is happening and what is being checked for. The same code in straight selenium is quite a bit more verbose.

\todo{INCLUDE SELENIUM CODE TO DO THIS HERE}
